Finding Quality Issues in SKOS Vocabularies

### 2012-03-23 analysis.tex
added results

With qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, we provide a reference implementation of the previously introduced quality checking functions and a freely-available open source tool for assessing the quality of a given SKOS vocabulary and finding possible quality issues. Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform. As a result, they obtain detailed reports listing possibly affected resources alongside with the potential cause of the issue. qSKOS is implemented in Java and can be used as standalone command-line tool or API in any other application. Its design is open for the introduction of additional quality functions.

@@

\begin{table}[h]
\label{tab:vocs}
\caption{Analyzed vocabularies}
\centering
\begin{tabular}{p{6cm}ccccccc}
\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & ? & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & ? & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings (MeSH) & ? & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base (PXV) & ? & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Eurovoc & ? & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary (IPSV) & ? & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
\hline
AGROVOC & 1.3 & 32035 & 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & ? & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & 2011/02/24 & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People (NYTP) & 2010/06/22 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings (LCSH) & ? & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Meketre & 2011/07/07 & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics (STW) & 8.06 & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System (NAICS) & 2012 & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
\hline
Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

@@

Results have been generated by using the qSKOS tool against the previously

\begin{table}[h]
\label{tab:results}
\caption{Results of the quality checking functions (cardinality of the result set)}
\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags &&&&&&& 0 & tba & 1224 & 0 & tba & 0 & 2 & 0 & 13411 \\

Incomplete Language Coverage &&&&&&& 32035 & tba & 0 & 0 & tba & 420 & 6456 & 0 & 0 \\

Undocumented Concepts &&&&&&& 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

Label Conflicts &&&&&&& 2949 & tba & 0 & 0 & tba & 4 & 5 & 0 & 13 \\

>>>>

We implemented the qSKOS tool that can be used for computing the quality checking functions introduced in \ref{sec:criteria} and made it publicly available\footnote{\url{https://github.com/cmader/qSKOS/}}. All data in the Tables \ref{tab:vocs} and \ref{tab:results} have been obtained by utilizing this tool. However, qSKOS is not only capable of returning numeric values, but can also provide a detailed report listing all resources returned by the quality checking functions alongside with the potential cause of the issue.

@@

\begin{table}[h]
\label{tab:vocs}
\caption{Analyzed vocabularies}
\centering
\begin{tabular}{p{6cm}ccccccc}
\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 & 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & 2.2.1 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings (MeSH) & ? & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base (PXV) & 1.6 & 2112 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Eurovoc & 5.0 & 6797 & 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 & 7945 & 13843 & 4483 & 3 & 0 \\
\hline
AGROVOC & 1.3 & 32035 & 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & ? & 743410 & 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & 2011/02/24 & 1125 & 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People (NYTP) & 2010/06/22 & 4979 & 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings (LCSH) & ? & 459182 & 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Meketre & 2011/07/07 & 422 & 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics (STW) & 8.06 & 6524 & 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System (NAICS) & 2012 & 4175 & 0 & 8684 & 2235 & 1 & 0 \\
\hline
Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 & 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

@@

\begin{table}[h]
\label{tab:results}
\caption{Results of the quality checking functions (cardinality of the result set)}
\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags & 0 & 0 && 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\

Incomplete Language Coverage & 0 & 0 && 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\

Undocumented Concepts & 96850 & 0 && 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

Label Conflicts & 12404 & 18 & 0 & 7 & n/a & 0 & 2949 & 0 & 0 & 0 & tba & 4 & 5 & n/a & 13 \\
